%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {MLOptic} % Organization
    {Chon Buri, Thailand} % Location
    {August 2022 - Present} % Date(s)
    {Skill: CMake · C++ · Qt · Linux · OpenCV · Git · Jira · Python Programming Language · Github action · Continuous Integration and Continuous Delivery (CI/CD) · vcpkg · OpenCL · KiCAD · Printed Circuit Board (PCB) Design · Docker · Go (Programming Language) · Angular · OpenCL Programming} % Skill
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Directed Software and Electrical teams to deliver integrated software-hardware solutions; mentored team, conducted code reviews, and enforced best practices.}
      \item {Framework Optimization: Architected scalable Qt/C++ frameworks, enhancing code maintainability and reusability, cutting test time from 2.45 hours to 45 minutes.}
      \item {Image Processing: Developed and optimized OpenCV/OpenCL, improving performance and accuracy for real-time applications.}
      \item {Full-Stack Development: Designed and developed a Manufacturing Execution System (MES) from scratch as micro services using Angular for frontend, GoLang for backend, MySQL for database, Minio for object storage, and Cypress for comprehensive end-to-end testing.}
      \item {Pipeline \& Repository Management: Configured GitLab/GitHub with CI/CD pipelines, access controls, and branching strategies, streamlining workflows and ensuring code quality.}
      \item {Containerization: Implemented Docker for consistent C++ and Qt compilation, minimizing build discrepancies across environments.}
      \item {Dependency Streamlining: Integrated VCPKG into CI/CD pipelines for efficient C++ package management, accelerating build processes.}
      \item {Infrastructure Setup: Deployed and managed GitLab server, MinIO server for object storage, and NGINX for reverse proxy.}
      \item {PCB Design \& Validation: Designed and validated PCB layouts for high-speed signals, including USB 3.0, ensuring performance and reliability compliance.}
      \item {Network Security: Strengthened security with firewalls, VPNs, and routing policies, protecting assets.}
      \item {DNS \& Collaboration: Administered DNS servers for domain/subdomain configurations; set up secure shared folders with access controls for collaboration.}
      \item {Website Deployment: company website, managing domain, hosting, and maintenance.}
      \item {Knowledge Management: centralized wiki server to enhance documentation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full Stack Developer | Part-time} % Job title
    {Krungthai Bank} % Organization
    {Bangkok, Thailand} % Location
    {June 2022 - Dec 2022} % Date(s)
    {Skill: Angular · TypeScript · Golang Programming Language · Gin · MySQL · Sequelize · Cypress · Docker · Kubernetes · Rancher · CI/CD · OWASP · JWT · Microservices} % Skill
    {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed scalable web application using Angular (frontend) and Golang with Gin (backend, microservices).}
      \item {Managed MySQL database with Sequelize migrations for schema consistency.}
      \item {Implemented Cypress for end-to-end testing, ensuring robust user flows.}
      \item {Configured Docker/Kubernetes for SIT/UAT deployments with CI/CD pipelines, managed via Rancher for streamlined cluster operations.}
      \item {Guided team on secure design, enforcing OWASP standards, JWT authentication, and API security.}
    \end{cvitems}
  }

%---------------------------------------------------------
  \cventry
    {Software/Test Engineer} % Job title
    {Magnecomp} % Organization
    {Wang Noi, Ayutthaya, Thailand} % Location
    {August 2021 - June 2022} % Date(s)
    {Skill: C\# · WinForms · Cognex Image Processing · Linear Regression · LCR Impedance Measurement · S-parameter Analysis · RF PCB Design · 50-ohm Transmission Lines} % Skill
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed robust C\# software for an automation machine, enabling precise control of X, Y, Z motors to interact with devices under test, integrated with Cognex-based image processing for enhanced accuracy and reliability.}
      \item {Implemented image calibration algorithms utilizing linear regression to ensure high-precision alignment and consistent performance in automated testing environments.}
      \item {Enhanced the stability of an LCR impedance measurement test station by optimizing S-parameters and reducing the system noise floor, resulting in improved measurement accuracy and reliability.}
      \item {Designed and implemented a self-validation test system leveraging S-parameter analysis to evaluate insertion loss, ensuring system integrity and performance consistency.}
      \item {Engineered an RF switching PCB with 50-ohm transmission lines, adhering to high-frequency design standards to minimize signal loss and ensure optimal RF performance.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Design/Test/Software Engineer} % Job title
    {Fabrinet} % Organization
    {Kookot, Lumlookka Patumthanee, Thailand} % Location
    {April 2018 - July 2021} % Date(s)
    {Skill: C\# · VB.NET · GoLang · WinForms · WPF · MVVM pattern · Asynchronous programming · MySQL · KiCad · PCB Design · Fiber Optics · High-frequency (THz) · SPI · I2C · MDIO · Mach-Zehnder modulator} % Skill
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Partnered with customers to design NPI processes for CFP2, Lidar, and Bidi, covering design, testing, deployment, debugging, software, PCBs, and databases.}
        \item {Built C\#, VB.NET, and GoLang software to analyze production failures, enabling quick defect resolution.}
        \item {Developed fiber optic testers using I2C and MDIO protocols with C\#/VB.NET (WinForms, WPF) for accurate validation.}
        \item {Optimized software, cutting test times by 10–200\% through efficient algorithms.}
        \item {Improved software stability with asynchronous programming for high-throughput testing.}
        \item {Designed PCBs for test stations using KiCad to meet reliability needs.}
        \item {Analyzed THz-frequency PCB failures, enhancing signal integrity.}
        \item {Upgraded test programs to visualize Mach-Zehnder modulator phase, aiding failure analysis.}
        \item {Created MySQL database to track production data for process monitoring.}
        \item {Built CoC unit pairing program to optimize yield via power balance.}
        \item {Reduced spreadsheet loading from 20s to 1s for power, testing, welding, and alignment.}
        \item {Designed PCBs to improve Gage R\&R test reliability.}
        \item {Analyzed optical failures to boost yield and performance.}
        \item {Enhanced test programs for efficiency and accuracy.}
        \item {Debugged PCBs, coordinating SMT rework for compliance.}
        \item {Developed MDIO-based test program for pre-stage CFP2-ACO components.}
        \item {Designed jigs, fixtures, and PCBs for 800µm device wire bonding and burning.}
        \item {Engineered high-temperature PCBs with wire bonding for burning process power supply.}
        \item {Optimized lens alignment to maximize power, minimize loss, and reduce time using mathematical modeling.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {BOMBARDIER} % Organization
    {Klongton, Klontoey Thailand} % Location
    {August 2017 - March 2018} % Date(s)
    {Skill: C · C++ · Python · TCL · Makefile · Shell Script · cmocka · Event Loop Programming · Asyncio · Asynchronous Programming · GDB · Git · Socket Communication · CentOS · Linux · SIL4} % Skill
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Initially served as a Test Engineer, later transitioning to a Software Designer/Developer/Implementer role, delivering critical solutions for the CITYFLO 650 project and platform screen door control systems.}
      \item {Developed simulations for train data, wayside communication, and regional automatic train operation data to test Region Automatic Train Protection (RATP) in the CITYFLO 650 project, leveraging Python, TCL, shell scripting, C, GDB, GIT, socket communication, asynchronous I/O, and event loops on CentOS.}
      \item {Designed and implemented test cases to validate system functionality and performance.}
      \item {Rearchitected simulated train data framework, transitioning from synchronous to asynchronous programming, reducing test execution time from 12 hours to 8 hours and mitigating random failures caused by Python’s Global Interpreter Lock (GIL).}
      \item {Configured GNU/Linux (CentOS) environments and designed test software architectures to support testing of platform screen door control systems, adhering to SIL4 safety requirements.}
      \item {Developed, designed, and implemented a platform screen door control system using C++, asynchronous I/O, and event loops, ensuring robust and safe operation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Test \& Software Engineer} % Job title
    {Fabrinet} % Organization
    {Kookot, Lumlookka Patumthanee, Thailand} % Location
    {May 2016 - July 2017} % Date(s)
    {Skill: C\# · VB.NET · VB6 · C++ · Perl · WinForms · RS232 · Fiber Optics · TX/RX Testing · Eye Diagram Analysis · EDFA · VNA · Statistical Methods · Database Design} % Skill
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
       \item {Contributed to the New Product Introduction (NPI) team at Fabrinet Thailand, focusing on fiber optic test process development, test instrument setup, tester deployment, software debugging, process optimization, and software development using C\#, VB.NET, C++, VB6, and Perl.}
       \item {Developed a Perl-based tool to parse raw production line test data and integrate it into the Fabrinet database system, ensuring accurate data management.}
       \item {Created a VB6 tool to control a PCB CNC router via RS232, interfacing with the Fabrinet database to select only functional device units for cutting, reducing human error and cutting time compared to the previous method of processing all units.}
       \item {Maintained Fiber Test Stations, performing TX/RX testing, eye diagram analysis, gain adjustments to meet eye diagram requirements, and Gage R\&R evaluations to ensure station reliability.}
       \item {Facilitated the transfer of fiber optic transceiver test processes from the R\&D stage (Canada customer) to the manufacturing stage at Fabrinet Thailand, ensuring seamless scalability.}
       \item {Planned and executed test instrument setup at Fabrinet Thailand to support production requirements.}
       \item {Maintained Photonic Wafer/Die testing machines, performing EDFA calibration, system insertion loss calibration, VNA instrument calibration, and failure analysis for wafer/die testing.}
       \item {Supported Wafer/Die Test Stations with RF testing using VNA equipment, ensuring high-precision measurements.}
       \item {Applied statistical methods to test machines, optimizing processes and reducing test times.}
       \item {Collaborated with Fabrinet IT to configure customer network infrastructure and design databases for customer product data, enhancing traceability and production efficiency.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Firmware Engineer} % Job title
    {Western Digital} % Organization
    {Bangpa-in, Thailand.} % Location
    {October 2013 - April 2016} % Date(s)
    {Skill: C · SVN · Perl · GCC · ARMCC · Makefile · Ubuntu · Embedded Systems · JTAG Debugging · Binary Analysis · Hard Disk · SATA · Vendor Specific Commands (VSC) · Firmware Development} % Skill
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Served as a key engineer specializing in Vendor Specific Commands (VSCs), leveraging advanced C programming to develop specialized commands for hard disk drive management, supporting cross-departmental objectives and innovation.}
        \item {Designed, implemented, and developed new Vendor Specific Commands (VSCs) per vendor requirements, collaborating with Controller, Servo, Channel, and Process departments to ensure seamless integration and functionality.}
        \item {Debugged back-end firmware and embedded software using JTAG-based debuggers, ensuring robust performance and reliability.}
        \item {Created a Perl-based tool to parse and decode binary code, simplifying failure analysis for Firmware, Process, and Failure Analysis (FA) teams across USA and Asia, with compatibility for both Windows and GNU/Linux environments.}
        \item {Utilized C, Subversion (SVN), Perl, GCC, ARMCC, and Makefiles extensively to deliver high-quality, maintainable code for embedded systems.}
        \item {Designed, implemented, and developed a patented solution: "Methods to Detect Thermal Asperity on Another Surface of Media When the Seeking Head is Unable to Stay on the Target Track," enhancing drive reliability and performance.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
